Analyzing the impact of social attributes on the success of commit integration

### 2017-02-18 Paper/MSRChallenge2017.tex
adjusted the todos

\textbf{Related work:}
Similar studies have shown the relationship between different attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al~\cite{tsay14icse} performed a very relevant study where they 
determine that the social connection between the developer who is asking the 
pull request and the integrators is a key factor torwards acceptance of a pull 
request. Unlike this previous study, in our study we look at a broader aspect of 
social aspects and how this attributes towards the success in Travis CI jobs. 
Gousios et al~\cite{gousios14} study the relationship between the area of the 
source code being modified by the developer requesting the changes to be pulled 
and the acceptance rate of these changes is highly correlated. Also existence of 
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request. Bettenburgh et 
al~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al~\cite{vasilescu14} explored how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated to the automatic build process. Yu et al~\cite{yu16} 
analyze the impact of CI usage in Github and its correlation with software 
quality. Unlike the works previously listed, our study focuses on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

@@

After building the data set, we converted the various Travis build statuses to
successful (passed in the data set) or not successful (errored, failed, canceled
and started in the data set).  This still left a big discrepancy in the two
categories, with about a 3:1 successful to not successful ratio. To avoid having
this discrepancy alter our results, we created a separate data set where the
successful builds were randomly selected until the number of successful builds
equaled the number of not successful builds (downsampled\todo{citation needed}).  We used both the
downsampled and non-downsampled data sets in our results.

>>>>

\textbf{Related work:}
Similar studies have shown the relationship between different attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al~\cite{tsay14icse} performed a very relevant study where they 
determine that the social connection between the developer who is asking the 
pull request and the integrators is a key factor torwards acceptance of a pull 
request. Unlike this previous study, in our study we look at a broader aspect of 
social aspects and how this attributes towards the success in Travis
CI\todo{citation needed for Travis CI} jobs. 
Gousios et al~\cite{gousios14} study the relationship between the area of the 
source code being modified by the developer requesting the changes to be pulled 
and the acceptance rate of these changes is highly correlated. Also existence of 
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request. Bettenburgh et 
al~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al~\cite{vasilescu14} explored how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated to the automatic build process. Yu et al~\cite{yu16} 
analyze the impact of CI usage in Github and its correlation with software 
quality. Unlike the works previously listed, our study focuses on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

@@

After building the data set, we converted the various Travis build statuses to
successful (passed in the data set) or not successful (errored, failed, canceled
and started in the data set).  This still left a big discrepancy in the two
categories, with about a 3:1 successful to not successful ratio. To avoid having
this discrepancy alter our results, we created a separate data set where the
successful builds were randomly selected until the number of successful builds
equaled the number of not successful builds (downsampled\todo{citation needed
for down sampling}).  We used both the
downsampled and non-downsampled data sets in our results.
